bad forecast good decision

### 2020-07-02 notebook/bad-forecast-good-decision.Rmd
re-run
use large r to highlight poor forecast performance

```{r}
library(tidyverse)
library(MDPtoolbox)
library(expm)
```

@@

# K is at twice max of f3; 8 * K_3 / 5
f1 <- function(x, h = 0, r = 1, K = 10 * 8 / 5){
  s <- pmax(x - h, 0)
  s + s * (r * (1 - s / K) )
}
f2 <- function(x, h = 0, r = 1, K = 10){
  s <- pmax(x - h, 0)
  s + s * (r * (1 - s / K) )
}

@@

```{r}
d <- map_dfc(models, function(f) f(states) - states) %>% mutate(state = states)
d %>% pivot_longer(names(models), "model") %>%
  ggplot(aes(state, value, col=model)) +
  geom_point() + 
  geom_hline(aes(yintercept = 0)) + 
  coord_cartesian(ylim = c(-5, 5), xlim = c(0,16))
```

Comparing forecasts

@@

opt <- sqrt(mean((true_sim$x - 10)^2))
```

@@

```{r}
d <- map_dfc(models, function(f) f(states) - states) %>% mutate(state = states)
d %>% pivot_longer(names(models), "model") %>%
  ggplot(aes(state, value, col=model)) +
  geom_point() + 
  geom_hline(aes(yintercept = 0)) + 
  coord_cartesian(ylim = c(-1, 5), xlim = c(0,16))
```

@@

sims <- map_dfr(names(transitions), 
                function(m){
                  policy <- policies %>% filter(model == m) %>% pull(policy)
                  map_dfr(1:reps, 
                          function(i){

                            mdp_planning(transitions[[true_model]], reward, discount,
                                     policy = policy, x0 = x0, Tmax = Tmax) %>%

                              select(value, state, time)  %>% 
                              mutate(state = states[state]) # index->value
                            },
                          .id = "reps")
                },
                .id = "model")

@@

@@

>>>>

```{r}
library(tidyverse)
library(MDPtoolbox)
library(expm)
library(mdplearning) # remotes::install_github("boettiger-lab/mdplearning")
```

@@

# K is at twice max of f3; 8 * K_3 / 5
f1 <- function(x, h = 0, r = 2, K = 10 * 8 / 5){
  s <- pmax(x - h, 0)
  s + s * (r * (1 - s / K) )
}
f2 <- function(x, h = 0, r = 1, K = 10){
  s <- pmax(x - h, 0)
  s + s * (r * (1 - s / K) )
}

@@

```{r}
d <- map_dfc(models, function(f) f(states) - states) %>% mutate(state = states)
d %>% pivot_longer(names(models), "model") %>%
  ggplot(aes(state, value, col=model)) +
  geom_point() + 
  geom_hline(aes(yintercept = 0)) + 
  coord_cartesian(ylim = c(-5, 8), xlim = c(0,16))
```

@@

opt <- sqrt(mean((true_sim$x - 10)^2))
opt
```

@@

@@

sims <- map_dfr(names(transitions), 
                function(m){
                  policy <- policies %>% filter(model == m) %>% pull(policy)
                  map_dfr(1:reps, 
                          function(i){
                            mdp_planning(transitions[[true_model]], reward, discount,
                                     policy = policy, x0 = x0, Tmax = Tmax) %>%
                              select(value, state_index = state, time, action_index = action)  %>% 
                              mutate(state = states[state_index]) # index->value
                            },
                          .id = "reps")
                },
                .id = "model")

@@

Note that the pattern is not driven merely be differences in the unfished equilibrium.  Compare forecast performance under management:

```{r}
scores <- sims %>%
  mutate(next_state = dplyr::lead(state_index), model = as.integer(model)) %>%
  select(time, state_index, next_state, action_index, model, reps) %>% 
  rowwise() %>%
  mutate(prob =  transitions[[model]][state_index, next_state, action_index] )

scores %>% 
  group_by(reps, model) %>%
  summarise(score = sum(log(prob))) %>%
  group_by(model) %>% summarise(mean_score = mean(score))

@@

```{r}
```
